---
title: "Analysis: Reliability Inference, Study 2"
author: "Victor Moreno"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = FALSE)
library(tidyverse)
library(jsonlite)
```

This notebook reads the CSVs written by `npm run export`. The experiment id is read from
`EXPERIMENT.id` in `experiment.js`, so there is nothing to change here between runs. It is a data check and
descriptive summary; the confirmatory analyses live in the reliability-inference repo.

## Load data

`trials.csv` is long format: one row per jsPsych trial. Columns that hold objects (the survey
plugin's `response`) are JSON strings.

```{r load}
exp_src <- readLines(file.path("..", "experiment.js"))
experiment_id <- sub('.*id:\\s*"([^"]+)".*', "\\1", grep('^\\s*id:\\s*"', exp_src, value = TRUE)[1])
raw_dir <- file.path("..", "data", "raw", experiment_id)

participants <- read_csv(file.path(raw_dir, "participants.csv"), show_col_types = FALSE)
trials <- read_csv(file.path(raw_dir, "trials.csv"), show_col_types = FALSE)
errors <- read_csv(file.path(raw_dir, "errors.csv"), show_col_types = FALSE)
```

## Completion and assignment

No exclusion rule is coded yet. Only completed sessions are kept; add any preregistered rule here.

```{r completion}
complete <- participants |> filter(completed)
message("Participants: ", nrow(participants), " started / ", nrow(complete), " completed.")

# Assignment balance: sessions per cell, and the counterbalancing factors.
assign <- trials |>
  filter(participant_id %in% complete$participant_id) |>
  distinct(participant_id, cell, chart_version, question_class, screen_order,
           result_order, fc_option_order, comprehension_disease)
assign |> count(cell)
assign |> count(chart_version, question_class)

# Comprehension check attempts (repeats until correct).
trials |>
  filter(task == "comprehension", participant_id %in% complete$participant_id) |>
  group_by(participant_id) |>
  summarise(attempts = n(), .groups = "drop") |>
  count(attempts)
```

## Responses by cell

`belief_common` is the belief response reverse-coded to the more common disease class (0-100).
`reliability` is the judged probability that the test identifies the disease (0-100).

```{r responses}
resp <- trials |>
  filter(participant_id %in% complete$participant_id,
         task %in% c("belief_initial", "belief_final", "reliability")) |>
  mutate(value = if_else(task == "reliability", as.numeric(response), as.numeric(belief_common))) |>
  select(participant_id, cell, task, value) |>
  pivot_wider(names_from = task, values_from = value) |>
  mutate(belief_change = belief_final - belief_initial)

resp |>
  group_by(cell) |>
  summarise(n = n(),
            initial = mean(belief_initial), final = mean(belief_final),
            change = mean(belief_change), reliability = mean(reliability),
            .groups = "drop")

if (nrow(resp) > 0) {
  resp |>
    pivot_longer(c(belief_initial, belief_final), names_to = "phase", values_to = "belief") |>
    mutate(phase = factor(phase, c("belief_initial", "belief_final"), c("Initial", "Final"))) |>
    ggplot(aes(phase, belief, group = participant_id)) +
    geom_line(alpha = 0.2) +
    stat_summary(aes(group = 1), fun = mean, geom = "line", linewidth = 1.2, colour = "#3E7C91") +
    facet_wrap(~ cell) +
    labs(x = NULL, y = "Belief in more common class (%)") +
    theme_minimal()
}
```

## Forced choice (Conflict cells)

```{r forced-choice}
trials |>
  filter(task == "forced_choice", participant_id %in% complete$participant_id) |>
  mutate(chose_common_class = as.logical(chose_common_class)) |>
  group_by(cell) |>
  summarise(n = n(), prop_chose_common_class = mean(chose_common_class), .groups = "drop")
```

## Data quality

```{r errors}
if (nrow(errors) > 0) {
  errors |> select(any_of(c("at", "uid", "trial_index", "message"))) |> head(20)
} else {
  message("No client-side errors were reported.")
}
```

## Session info

```{r session}
sessionInfo()
```
